---
title: "Centraldog"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Centraldog}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Centraldog)
```

## Description

The package is about the centrla dogma of molecular biology. The package includes 5 distint functions: "generate_random_dna_sequence", "transcript", "DNA_codons", "prot_seq" and "plot_amino_acid_counts".

### Function demonstration

#### generate_random_dna_sequence

The function generates a DNA sequence of a give length:

```{r}
DNA <- generate_random_dna_sequence(100)
DNA
```

#### transcript

The function transcripts the DNA sequnce to RNA sequence:

```{r}
RNA <- transcribe(DNA)
RNA
```

#### DNA_codons

The function splits the sequence into codons.

```{r}
codons <- DNA_codons(RNA)
codons
```

#### prot_seq

The function translate codons into amino acids.

```{r}
amino_acids <- prot_seq(codons)
amino_acids
```

#### plot_amino_acid_counts

The function the amino acids counts into bar plot

```{r}
plot_amino_acid_counts(amino_acids)
```
